---
title: "Exploratory Analysis - WA Super Datasets"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r message=FALSE}
library(GGally)
library(zoo)
library(mondate)
library(lubridate)
library(tidyr)
library(doBy)
library(geepack)
library(klaR)
library(rattle)
library(caret)
```

# MERGE DATA (warning: actual data chunks in Part 1)

```{r}
MergeMain <- function(df1, df2){
  #do left outer join
  df3 <- merge(df1, df2, by.x="Client.Number.key", by.y="Client.No", all.x=TRUE)
  #change all NA values to 0, ncol(df3) leads to the last col in the df
  df3[ is.na(df3[,ncol(df3)]), ncol(df3) ] <- "0"
  return(df3)
}
```

```{r Merge using function}
merge1 <- MergeMain(MemberData, occurBenefit)
merge1 <- MergeMain(merge1, occurCall)
merge1 <- MergeMain(merge1, occurEmail)
merge1 <- MergeMain(merge1, occurClicks)
merge1 <- MergeMain(merge1, occurAOL)
merge1 <- MergeMain(merge1, occurRollins)
merge1 <- MergeMain(merge1, LGAPCount)
merge1 <- MergeMain(merge1, LGSPCount)
merge1 <- MergeMain(merge1, occurSOA)
merge1 <- MergeMain(merge1, occurAR)
```

# Create Main Dataset from merge1

```{r EDA}
EDA <- data.frame("ClientNo"=merge1$Client.Number.key,
                  "Status"=merge1$OverallStatus,
                  "Duration"=as.numeric(merge1$DurationinWS),
                  "Fund"=merge1$Fund,
                  "Gender"=merge1$Sex,
                  "Age"=merge1$Age,
                  "Lifestage"=merge1$Lifestage,
                  "Salary"=merge1$Salary,
                  "Balance"=as.numeric(merge1$FinalBalance),
                  "HasLGAP"=as.numeric(merge1$LGAPCount),
                  "HasLGSP"=as.numeric(merge1$LGSPCount),
                  "Insurance"=as.factor(merge1$Has.Insurance),
                  "BenefitPayments"=as.numeric(merge1$Benefit.Freq),
                  "CallFreq"=as.numeric(merge1$Call.Freq),
                  "EmailFreq"=as.numeric(merge1$Email.Freq),
                  "SuperClickAdvice"=as.numeric(merge1$Click.Freq),
                  "AOLFreq"=as.numeric(merge1$AOL.Freq),
                  "RollinsFreq"=as.numeric(merge1$Rollin.Freq),
                  "SOAFreq"=as.numeric(merge1$SOA.Freq),
                  "ARFreq"=as.numeric(merge1$AR.Freq),
                  "Voluntary"=as.factor(merge1$Members.Contributing.),
                  "SinceLastCon"=as.factor(merge1$Last.Contribution)
                  )
```

```{r List of client numbers that have multiples in EDA}
repeats <- data.frame(table(EDA$ClientNo))
repeats <- repeats[repeats$Freq>"1",]
```

```{r Create overall balance for multiple accounts using sum finalbalance}
for (i in 1:nrow(repeats)){
  Client <- repeats$Var1[i]
  MatchIdx <- which(EDA$ClientNo %in% Client)
  EDA$Balance[MatchIdx] <- sum(EDA$Balance[MatchIdx])
}
```

```{r getting rid of the other observations}
EDA <- EDA[firstobs(EDA[,1]),]
```

```{r To check if there is any N/A or 0 balance for Exit members}
summary(EDA$Balance[EDA$Status=="E"])
```

# Modelling with EDA (original dataset) PART 2

### EDA Decision Tree

```{r}
library(rpart)
library(rpart.plot)

dtmodel <- rpart(Status ~ . -ClientNo, data=EDA, method='class')
rpart.plot(dtmodel, extra=106)
```

```{r fig.height=6, fig.width=12.5}
dtmodel <- ctree(Status ~ Duration+Fund+Gender+Age+Lifestage+Salary+Balance+HasLGAP+HasLGSP+Insurance+BenefitPayments+CallFreq+EmailFreq+SuperClickAdvice+AOLFreq+RollinsFreq+SOAFreq+ARFreq+Voluntary+SinceLastCon, data=EDA)
plot(dtmodel)
```

### EDA Random Forest

```{r message=FALSE}
library(randomForest)
library(partykit)
library(party)
library(tree)
```

```{r}
rfmodel <- randomForest(Status ~ . -ClientNo, data=EDA[!is.na(EDA$Salary),])
print(rfmodel)
```

```{r EDA varImpPlot}
varImpPlot(rfmodel, main='Variable Importance based on Random Forest')
```

```{r}
ctable <- as.table(matrix(c(49536, 131, 92, 13997), nrow = 2, byrow = TRUE))
fourfoldplot(ctable, color = c("#CC6666", "#99CC99"),
             conf.level = 0, margin = 1, main = "Confusion Matrix RF EDA")
```


### EDA Logistic

```{r}
logmodel <- glm(Status ~ . - ClientNo, data=EDA, family = "binomial"(link="logit"))
summary(logmodel)
```

```{r}
anova(logmodel, test='Chisq')
```

### EDA LDA

```{r}
library(MASS)
library(klaR)
```

```{r}
ldamodel <- lda( Status ~ . -ClientNo, data=EDA)
```

```{r}
ldamodelvalues <- predict(ldamodel)
head(ldamodelvalues)

ldahist(ldamodelvalues$x[,1], g=EDA$Status)
```
```{r}
partimat(Status ~ . -ClientNo, data=EDA, method='lda')
```

# Making EDA2 less variables from EDA

```{r Narrowing variables down to top 7}
EDA2 <- data.frame("ClientNo"=merge1$Client.Number.key,
                  "Status"=merge1$OverallStatus,
                  "Duration"=as.numeric(merge1$DurationinWS),
                  "Age"=merge1$Age,
                  "Salary"=merge1$Salary,
                  "Balance"=as.numeric(merge1$FinalBalance),
                  "Insurance"=as.factor(merge1$Has.Insurance),
                  "BenefitPayments"=as.numeric(merge1$Benefit.Freq),
                  "SinceLastCon"=as.factor(merge1$Last.Contribution)
                  )
```

```{r List of client numbers that have multiples in EDA2}
repeats <- data.frame(table(EDA2$ClientNo))
repeats <- repeats[repeats$Freq>"1",]
```

```{r Create overall balance for multiple accounts using sum finalbalance}
for (i in 1:nrow(repeats)){
  Client <- repeats$Var1[i]
  MatchIdx <- which(EDA2$ClientNo %in% Client)
  EDA2$Balance[MatchIdx] <- sum(EDA2$Balance[MatchIdx])
}
```

```{r getting rid of the other observations}
EDA2 <- EDA2[firstobs(EDA2[,1]),]
```

```{r To check if there is any N/A or 0 balance for Exit members}
summary(EDA2$Balance[EDA2$Status=="E"])
```

# Training and Test EDA2

```{r Making the train and test dataset}
set.seed(95)
TestIdx <- sample(1:nrow(EDA2), size =floor(nrow(EDA2)*0.15))
EDA2Test <- EDA2[TestIdx,]
EDA2Train <- EDA2[-(TestIdx),]
```

### EDA2 Decision Tree

```{r fig.height=20, fig.width=40}
dtmodel <- ctree(Status ~ Duration+Age+Salary+Balance+Insurance+BenefitPayments+SinceLastCon, data=EDA2)
plot(dtmodel)
```

### EDA2 RandomForest

```{r RandomForest with Training Dataset}
A.rfmodel <- randomForest(Status ~ . -ClientNo, data=EDA2Train[!is.na(EDA2Train$Salary),], importance=TRUE, na.action=na.roughfix, ntree=300)
print(A.rfmodel)
```

```{r Prediction with test dataset}
predRF <- predict(A.rfmodel, newdata=EDA2Test)
table(predRF,EDA2Test$Status)
```
```{r confusion matrix default}
errormatrix(EDA2Test$Status, predRF, relative=TRUE)
```
```{r}
ctable <- as.table(matrix(c(7703, 18, 36, 2123), nrow = 2, byrow = TRUE))
fourfoldplot(ctable, color = c("#CC6666", "#99CC99"),
             conf.level = 0, margin = 1, main = "Confusion Matrix RF EDA2")
```

```{r ggVarImp plot}
ggVarImp(A.rfmodel, log=TRUE)
```

### EDA2 Random Forest Multiple Cross Validation

```{r}
#library(caret)
#train_control <- trainControl(method='cv', number=3)
#grid <- expand.grid(.fL=c(0), .usekernel=c(FALSE))
#rfcvmodel <- train(Status~.-ClientNo, data=EDA2[!is.na(EDA2$Salary),], trControl=train_control, method='nb')
#print(rfcvmodel)
```

```{r}
#predRF <- predict(rfcvmodel, newdata=EDA2Test)
#table(predRF,EDA2Test$Status)
```


### EDA2 LDA

```{r}
ldamodel <- lda( Status ~ . -ClientNo, data=EDA2Train)
```

```{r}
ldamodelvalues <- predict(ldamodel, newdata=EDA2Test)

ldahist(ldamodelvalues$x[,1], g=EDA2Test$Status)
```

```{r}
errormatrix(EDA2Test$Status, ldamodelvalues$class, relative=TRUE)
```

```{r}
par(mar=c(0.1,0.1,0.1,0.1))
partimat(Status ~ BenefitPayments+SinceLastCon+Duration+Balance, data=EDA2, method='lda')
```


# GEE Model

```{r}
geefit <- geeglm(Status~Duration+Gender+Age, id=ClientNo, data=EDA, family=binomial, corstr = "exchangeable")
```

can try gee aswell, change the corstr

```{r}
summary(EDA)
#EDA$Salary[is.na(EDA$Salary)] <- 0
```


