---
title: "Hydrocarbon in Place"
author: "Yanan Cheah & Amanda Efendi"
date: "23/05/2019"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(mc2d)
library(EnvStats)
library(corrplot)
```

#DISTRIBUTIONS FOR THE PARAMETER

## NTG with Triangular distribution

```{r}
# Net to Gross
#plot(seq(0.704761905,1, by=0.001),dtriang(seq(0.704761905,1, by=0.001), min=0.704761905, mode=0.881, max=1), type='h', main='Distribution of NTG values', ylab='density', xlab='NTG values')
```

## GRV With Triangular distribution

```{r}
# GRV
#plot(seq(2352,4368), dtri(seq(2352,4368), min=2352, mode=3360, max=4368), type='h', ylab='density??', xlab='GRV Values/e+05', main='Distribution of GRV values')
```

## POR With normal distribution

```{r}
# POR is porosity
#par(pty='m') 
#plot(seq(0.15,0.245, by=0.001), dnorm(seq(0.15,0.245,by=0.001), mean = 0.1985, sd = 0.0136), type='h', lty=1.5, ylab='Density', xlab='Porosity values', main='Distribution of porosity')
```


#PART 1 - SIMULATE GIIP FOR 1 FIELD

##FORMULA TO FIND GIIP

$$
GIIP = (GRV*NTG*POR*SAT*35.3)/BG
$$

Don't forget to times 10^5 as GRV was divided by 10^5 intially.

##CORE FUNCTION
```{r}
#GRV_p1=c(2352,3360,4368)
#NTG_p1=c(0.704761905,0.881,1)
#POR_p1=c(0.1985,0.0136) #ASSUMPTION: medium value is the mu
#SAT_p1=c(0.72, 0.8, 0.88)
```

```{r}
#CORE FUNCTION
set.seed(127)

simulate <- function(grv, ntg, por, sat){
  GIIP = NULL
  
  for (i in 1:1000){
  GRV <- rtri(1, min=grv[1], mode=grv[2], max=grv[3])*10^5
  NTG <- rtri(1, min=ntg[1], mode=ntg[2], max=ntg[3])
  POR <- rnorm(1, mean=por[1], sd=por[2])
  SAT <- rtri(1, min=sat[1], mode=sat[2], max=sat[3])
  BG <- 0.004
  
  GIIP[i] <- (GRV*NTG*POR*SAT*35.3)/BG
  }
  
  return(GIIP)
}

```

##WRAPPER FUNCTION 1 - SIMULATE FOR ALL FIELDS
```{r}
##WRAPPER FUNCTION 2
#Store all GRV parameters for 5 fields into 1 vector, etc

GRV_p <- matrix(data=c(2352,3360,4368,9534,13620,17706,2393,3290,4277,2114,3020,3926,2709,3870,5031), nrow=5, ncol=3, byrow=TRUE)
NTG_p <- matrix(data=c(0.704761905,0.881,1,0.464,0.58,0.696,0.536,0.67,0.804,0.7576,0.947,1,0.62,0.775,0.93), nrow=5, ncol=3, byrow=TRUE)
POR_p <- matrix(data=c(0.1985,0.0136,0.2286,0.0134,0.2052,0.0126,0.2181,0.0197,0.2286, 0.0134), nrow=5, ncol=2, byrow=TRUE)
SAT_p <- matrix(data=c(0.7,0.8,0.9,0.65,0.75,0.85,0.65,0.75,0.85,0.6,0.7,0.8,0.75,0.85,0.95), nrow=5, ncol=3, byrow=TRUE)
BG_p <- 0.004

set.seed(127)

getall_GIIP <- function(){
  all_GIIP = NULL
  
  for (i in 1:5){
    GIIP <- simulate(GRV_p[i,], NTG_p[i,], POR_p[i,], SAT_p[i,])
    all_GIIP <- cbind(all_GIIP,GIIP)
  }
  return(all_GIIP)
}
```

###Test wrapper function - done
```{r}
set.seed(127)
GIIP_all <- getall_GIIP()
colnames(GIIP_all) <- c("GIIP_Mung","GIIP_LBG","GIIP_Murr","GIIP_Oxf","GIIP_Nimb")
set.seed(127)
test <- simulate(GRV_p[1,], NTG_p[1,], POR_p[1,], SAT_p[1,])
```

##Regression formula for GIIP
$$
GIIP_{Mung} = c + \theta_{GRV} X_{GRV} + \theta_{NTG} X_{NTG} + \theta_{POR} X_{POR} + \theta_{SAT} X_{SAT}
$$

#PART 2 - AGGREGATION

GIIPref: GRV medium value
GIIPlo: GRV low value
GIIPhi: GRV high value

swing for grv is GIIPhi - GIIPlo

repeat for other variables :)

```{r}
swingGRV <- function(){
  swGRV = NULL
  
  for (i in 1:3){
    GIIPref <- (GRV_p[i,2]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    GIIPlo <- (GRV_p[i,1]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    GIIPhi <- (GRV_p[i,3]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    swGRVi = GIIPhi - GIIPlo
    swGRV[i] = swGRVi
    }
  return(swGRV)
}

swingNTG <- function(){
  swNTG = NULL
  
  for (i in 1:3){
    GIIPref <- (GRV_p[i,2]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    GIIPlo <- (GRV_p[i,2]*NTG_p[i,1]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    GIIPhi <- (GRV_p[i,2]*NTG_p[i,3]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    swNTGi = GIIPhi - GIIPlo
    swNTG[i] = swNTGi
    }
  return(swNTG)
}

swingPOR <- function(){
  swPOR = NULL
  
  for (i in 1:3){
    GIIPref <- (GRV_p[i,2]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    GIIPlo <- (GRV_p[i,2]*NTG_p[i,2]*(POR_p[i,1]-(2*POR_p[i,2]))*SAT_p[i,2]*35.3)/BG_p
    GIIPhi <- (GRV_p[i,2]*NTG_p[i,2]*(POR_p[i,1]+(2*POR_p[i,2]))*SAT_p[i,2]*35.3)/BG_p
    swPORi = GIIPhi - GIIPlo
    swPOR[i] = swPORi
    }
  return(swPOR)
}

swingSAT <- function(){
  swSAT = NULL
  
  for (i in 1:3){
    GIIPref <- (GRV_p[i,2]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,2]*35.3)/BG_p
    GIIPlo <- (GRV_p[i,2]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,1]*35.3)/BG_p
    GIIPhi <- (GRV_p[i,2]*NTG_p[i,2]*POR_p[i,1]*SAT_p[i,3]*35.3)/BG_p
    swSATi = GIIPhi - GIIPlo
    swSAT[i] = swSATi
    }
  return(swSAT)
}

```

##Calculate Swing of all variables for 3 fields
```{r}
swGRV <- swingGRV()
swNTG <- swingNTG()
swPOR <- swingPOR()
swSAT <- swingSAT()
    
all_swing = matrix(c(swGRV,swNTG,swPOR,swSAT), byrow = TRUE, nrow=4, ncol=3)  
colnames(all_swing) <- c("GIIP_Mung","GIIP_LBG","GIIP_Murr")
rownames(all_swing) <- c("GRV","NTG","POR","SAT")
```

##Calculating coefficients - theta
$$
\theta_{GRV}^i = \frac{S_{GRV}^i \times\sqrt{Var(GIIP_i)}}{  \sqrt{S_{GRV}^i+S_{NTG}^i+S_{POR}^i+S_{SAT}^i}}
$$
While the variable $i$ represents the field number.  

```{r}
theta <- function(){
  
  thetaMatrix = NULL
 
  
  for (i in 1:3){
    Variance <- var(GIIP_all[,i])
    Swings <- sum((all_swing[2,i])^2,(all_swing[3,i])^2,(all_swing[4,i])^2,(all_swing[1,i])^2)
    
    thetaGRV <- (all_swing[1,i]*sqrt(Variance))/sqrt(Swings)
    thetaNTG <- (all_swing[2,i]*sqrt(Variance))/sqrt(Swings)
    thetaPOR <- (all_swing[3,i]*sqrt(Variance))/sqrt(Swings)
    thetaSAT <- (all_swing[4,i]*sqrt(Variance))/sqrt(Swings)
    thetaMatrix <- cbind(thetaMatrix, c(thetaGRV,thetaNTG,thetaPOR,thetaSAT))
    
  }
  
  return(thetaMatrix)
}
```

```{r}
thetas <- theta()
colnames(thetas) <- c("GIIP_Mung","GIIP_LBG","GIIP_Murr")
rownames(thetas) <- c("GRV","NTG","POR","SAT")
```


##Finding Correlation
```{r}
correlation <- function(rho, column, column2){
  corr = NULL
  covariance = 0
  
  for (i in 1:4){
    covariance1 = rho*thetas[i,column]*thetas[i,column2]
    covariance = covariance + covariance1
  }
  
  corr = covariance/(sqrt(var(GIIP_all[,column])*var(GIIP_all[,column2])))

  return(corr)  
  
}
```

```{r}
MungLBG <- c(correlation(0,1,2),correlation(0.5,1,2),correlation(1,1,2))
MungMurr <- c(correlation(0,1,3),correlation(0.5,1,3),correlation(1,1,3))
LBGMurr <- c(correlation(0,2,3),correlation(0.5,2,3),correlation(1,2,3))
```



##Simulate GIIP with correlation
```{r}
# Estimating parameters for field Mungaroo
beta1 <- 1/(var(GIIP_all[,1])/mean(GIIP_all[,1]))
alpha1 <- mean(GIIP_all[,1])*beta1

# Estimating parameters for field LBG
beta2 <- 1/(var(GIIP_all[,2])/mean(GIIP_all[,2]))
alpha2 <- mean(GIIP_all[,2])*beta2

# Estimating parameters for field Murat
beta3 <- 1/(var(GIIP_all[,3])/mean(GIIP_all[,3]))
alpha3 <- mean(GIIP_all[,3])*beta3

```

```{r}
# matrix for rho = 0
matrho0 <-simulateMvMatrix(1000, 
                      distributions = c( GIIPMung= "gamma", GIIPLBG = "gamma",GIIPMurr = "gamma"), 
                      param.list =list(GIIPMung=list(shape=alpha1,scale=1/beta1), 
                                       GIIPLBG= list(shape=alpha2,scale=1/beta2),
                                       GIIPMurr= list(shape=alpha3,scale=1/beta3)), 
                      cor.mat = matrix(c(1, MungLBG[1],MungMurr[1],MungLBG[1], 1,LBGMurr[1],MungMurr[1],LBGMurr[1],1),3, 3,byrow = TRUE),
                      seed = 50)
```

```{r}
# matrix for rho = 0.5
matrho0.5 <-simulateMvMatrix(1000, 
                      distributions = c( GIIPMung= "gamma", GIIPLBG = "gamma",GIIPMurr = "gamma"), 
                      param.list =list(GIIPMung=list(shape=alpha1,scale=1/beta1), 
                                       GIIPLBG= list(shape=alpha2,scale=1/beta2),
                                       GIIPMurr= list(shape=alpha3,scale=1/beta3)), 
                      cor.mat = matrix(c(1, MungLBG[2],MungMurr[2],MungLBG[2], 1,LBGMurr[2],MungMurr[2],LBGMurr[2],1),3, 3,byrow = TRUE),
                      seed = 50)
```

```{r}
# matrix for rho = 1
matrho1 <-simulateMvMatrix(1000, 
                      distributions = c( GIIPMung= "gamma", GIIPLBG = "gamma",GIIPMurr = "gamma"), 
                      param.list =list(GIIPMung=list(shape=alpha1,scale=1/beta1), 
                                       GIIPLBG= list(shape=alpha2,scale=1/beta2),
                                       GIIPMurr= list(shape=alpha3,scale=1/beta3)), 
                      cor.mat = matrix(c(1, MungLBG[3],MungMurr[3],MungLBG[3], 1,LBGMurr[3],MungMurr[3],LBGMurr[3],1),3, 3,byrow = TRUE),
                      seed = 50)
```

##Aggregate Simulated GIIP Values
```{r}
GIIPTotal0 <- matrho0[,1]+matrho0[,2]+matrho0[,3]
hist(GIIPTotal0, col="lightsteelblue",main="Histogram of GIIP (rho=0)")
abline(v=quantile(GIIPTotal0, c(0.1, 0.5, 0.9)), lty=3)
```

```{r}
GIIPTotal0.5 <- matrho0.5[,1]+matrho0.5[,2]+matrho0.5[,3]
hist(GIIPTotal0.5, col="aquamarine2",main="Histogram of GIIP (rho=0.5)")
abline(v=quantile(GIIPTotal0.5, c(0.1, 0.5, 0.9)), lty=3)
```

```{r}
GIIPTotal1 <- matrho1[,1]+matrho1[,2]+matrho1[,3]
hist(GIIPTotal1, col="lightsalmon1",main="Histogram of GIIP (rho=1)")
abline(v=quantile(GIIPTotal1, c(0.1, 0.5, 0.9)), lty=3)
```
##Correlation Matrix
```{r}
corrmatrix1 <- matrix(c(1, MungLBG[3],MungMurr[3],MungLBG[3], 1,LBGMurr[3],MungMurr[3],LBGMurr[3],1),3, 3,byrow = TRUE)
corrmatrix0.5 <- matrix(c(1, MungLBG[2],MungMurr[2],MungLBG[2], 1,LBGMurr[2],MungMurr[2],LBGMurr[2],1),3, 3,byrow = TRUE)
corrmatrix0 <- matrix(c(1, MungLBG[1],MungMurr[1],MungLBG[1], 1,LBGMurr[1],MungMurr[1],LBGMurr[1],1),3, 3,byrow = TRUE)
```

```{r}
par(mfrow=c(2,2))
corrplot(corrmatrix1,method = 'square',type = 'upper',tl.col = 'black',order='hclust')
corrplot(corrmatrix0.5,method = 'square',type = 'upper',tl.col = 'black',order='hclust')
corrplot(corrmatrix0,method = 'square',type = 'upper',tl.col = 'black',order='hclust')
```



